---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rmsdown

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/vidonne/rmsdown/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/vidonne/rmsdown/actions/workflows/R-CMD-check.yaml)
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/rmsdown)](https://CRAN.R-project.org/package=rmsdown) -->
<!-- badges: end -->

Create high-quality, UNHCR-branded PDFs for Results Monitoring Surveys (RMS) with the `{rmsdown}` R package. This package leverages the `{pagedown}` framework to deliver consistent and professional reports aligned with **UNHCR’s brand guidelines**. Additionally, it includes a dedicated plot function for branded charts.

## Features

- A specialized R Markdown template for RMS reports
- Custom CSS styling with Bootstrap 5 integration
- A plot function for consistent and branded visualizations
- Alignment with UNHCR’s branding and guidelines


## Installation

Install the development version of `{rmsdown}` from GitHub with:

```{r, eval = FALSE}
# If pak is not yet installed, uncomment the following line:
# install.packages("pak")
pak::pkg_install("vidonne/rmsdown")
```
## Usage

### Getting Started

To use the `{rmsdown}` template, specify the `rmsdown::paged_report` format in the YAML header of your R Markdown file:

```yaml
---
title: "Results Monitoring Surveys"
subtitle: "Country Year"
output: rmsdown::paged_report
---
```

### Creating a New Document in RStudio

1. File → New File → R Markdown
2. Select “From Template”
3. Choose the **RMS Paged Report** template

### Custom CSS Classes

The `{rmsdown}` template incorporates Bootstrap 5 for styling. Refer to the [Bootstrap documentation](https://getbootstrap.com/docs/5.3/getting-started/introduction/) for details on available CSS classes.

For section-specific styling, use the following format:

```{r, eval = FALSE}

###### [1.]{.big-num} Introduction {.section-title}

# Introduction {.hide-h1}

## The Forced Displacement Survey

The following content starts here.

```

### Plot Functions

The package includes a plot function to help you create consistent and branded charts. More functions will be added in future updates.

```{r, eval = FALSE}
library(ggplot2)

df_percent <- data.frame(
  category = c("Category A", "Category B", "Category C", "Category D"),
  value = c(0.3, 0.08, 0.6, 0.75)
)

simple_bar_chart(df_percent, cat = "category", val = "value")
```

```{r child="man/rmdfragments/unhcr_tools.Rmd"}
```

## Acknowledgements

We extend our gratitude to the creators of the [`pagedown`](https://github.com/rstudio/pagedown) package that influenced the development of `{rmsdown}`.

## Contribution and Code of Conduct

Contributions to `{rmsdown}` are highly valued. To ensure a welcoming and inclusive community, we follow our [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). If you have suggestions, uncover bugs, or envision new features, kindly submit an [issue on GitHub](https://github.com/vidonne/rmsdown/issues).

## License

This package is distributed under the [MIT License](https://github.com/vidonne/rmsdown/blob/master/LICENSE.md).